---
title: "Bayesian Model"
author: "Ranajay"
output: word_document
---

Project Statement
=================
Star Technologies Company (STC) has been in the business of manufacturing remote
controllers for televisions and audio systems for two decades. It is now planning on entering the computer tablet market with a new product.

Obee Juan, Star's product development manager,has narrowed them down to
what he believes are the four most important: retail unit price, screen size, processor speed,and RAM.His qualitative results suggest that brand 
is also important to purchase consideration.

Obee develop a CBC task with the following five attributes:
Brand- 4 levels: STC, Somesong, Pear, Gaggle (level codes: 0,1,2,3)
Price- 3 levels: $199, $299, $399 (levels: 0,1,2)
Screen- 3 levels: 5 inch, 7 inch, 10 inch (levels: 0,1,2)
RAM- 3 levels: 8 Gb, 16 Gb, 32 Gb (Gb = "gigabytes") (levels: 0,1,2)
Processor- 3 levels: 1.5 GHz, 2 GHz, 2.5 GHz (GHz = "gigahertz") (levels: 0,1,2)

The task was designed to allow estimation of the two-way interaction between brand and price. 
It has 36 choice sets. Each choice set presented three alternatives, each described as specific combinations of attribute levels. 
Respondents picked from each choice set the alternative they most preferred, Alternative 1, 2, or 3.

Prerequisite Steps
===================

(A) stc-cbc-respondents-v3.RData - This is the respondent data in R file format. The variables in it are documented in the file stc-v3-datamap.txt. We will
load this file in R.

(B) stb-dc-task-cbc-v3.csv - This describes the choice task in attributes and levels; it's a tab-delimited csv file with a header record. 
The attribute levels are coded 0,1,2,3. They correspond to the descriptions of the attributes and levels provided in the assignment description document.

(C) extra-scenarios.csv - Descriptions of the additional choice scenarios that we will analyze after estimating your MNL model; 
a comma-delimited csv file.

(D) efCode.RData - A couple of R functions we will use to code your attributes and levels as the predictor variables you'll use in your MNL model; an R file.
We will load this file.

INITIALIZE
==========

```{r}
#setwd("C:/R_Working/") # Set your own working directory
require(dummies)
load("stc-cbc-respondents-v3.RData")
load("efCode.RData") 

str(efcode.att.f)
str(efcode.attmat.f)
str(resp.data.v3)

```
================= INITIALIZE ENDS ===================


=======================================================================
STEP1 - Starts              
=======================================================================

CREATING PREDICTOR VARIABLES
----------------------------

```{r}
taskV3 <- read.csv("stc-dc-task-cbc-v3.csv", sep="\t")

str(taskV3)
task.mat <- as.matrix(taskV3[, c("screen", "RAM", "processor", "price", "brand")])
dim(task.mat)
X.mat=efcode.attmat.f(task.mat)
dim(X.mat)

str(task.mat) # 5 columns; 108 rows
str(X.mat)  # 11 columns; 108 rows
head(task.mat)
head(X.mat)

```

Creation of interactive variable brand and price:
-------------------------------------------------
- Create a new price variable (a vector) by subtracting each price value from the mean price.
- Multiply this vector with each column in X.mat that represents brand (col 9:11). Create a matrix from 9:11 from X.mat
------------------------------------------------

```{r}
pricevec  <- taskV3$price-mean(taskV3$price)
X.brands  <- X.mat[,9:11] 
X.BrandByPrice <- X.brands*pricevec #Vector and Matrix Multiplication
X.matrix=cbind(X.mat,X.BrandByPrice) 
dim(X.matrix)
```

To verify matrix multiplication: X premultiplied by it's transpose is a square matrix. Determinant of the product will be a high positive number.%*% means matrix multiplication. X.matrix is the design matrix

```{r}
det(t(X.matrix)%*%X.matrix) #4.19695e+23: Verified Successfully

```

DEVELOP THE RESPONSE MATRIX
----------------------------

We need to get the responses that STC's survey participants provided to the 36 choice questions they answered. The are in the data frame resp.data-v3 that's in the R data file stc-cbc-respondents-v3.RData. The variable names are DCM1_1 through DCM1_36. They are the 4th through the 39th variables in resp.data-v3
---------------------------

```{r}
apply(resp.data.v3[4:39], 2, function(x){tabulate(na.omit(x))}) 
summary(resp.data.v3)
head(resp.data.v3) # 36 choices: DCM1_1 to DCM1_36 (col 4 to 39)
ydata=resp.data.v3[,4:39]
names(ydata)
ydata=na.omit(ydata) # Remove missing values
str(ydata)
ydata=as.matrix(ydata) # Convert to Matrix
head(ydata)
```


Creating Data Structure for MCMC
--------------------------------
We have our X matrix("X.matrix"), our choice responses (they're in ydata), and zowner, our indicator variable for STC product ownership.

lgtdata is a list of data for each respondent. Its length equals the number of respondents (424). (Lists have length.) The data for each respondent is a list with two elements, X.matrix and the respondent's choice responses, from their row in ydata.So, lgtdata is a list of lists.
--------------------------------

```{r}
lgtdata = NULL # a starter placeholder for your list 
for (i in 1:424) { 
	lgtdata[[i]]=list(y=ydata[i,],X=X.matrix) 
	} 

length(lgtdata)
lgtdata[[3]]
lgtdata[[4]]

str(lgtdata)

```

Fitting the HB Model (No Covariate) - MODEL1
--------------------------------------------

```{r}
require(bayesm)
Data1=list(p=3,lgtdata=lgtdata) # p:number of choice alternatives = 3 
mcmctest1=list(R=100000,keep=100)
set.seed(123)
testrun1=rhierMnlDP(Data=Data1,Mcmc=mcmctest1)

```
=======================================================================
STEP1 - Ends              
=======================================================================


=======================================================================
STEP2 - Starts              
=======================================================================


Analyzing Results (Model No Covariate) - MODEL1
-----------------------------------------------

```{r}
names(testrun1)
betadraw1=testrun1$betadraw
dim(betadraw1)
```

Determine Burn-In Period
------------------------
Based on the graph for 4 respondents:
Burn-In Period = 601

```{r}
#1st person
plot(1:length(betadraw1[1,1,]),betadraw1[1,1,])
plot(1:length(betadraw1[1,2,]),betadraw1[1,2,])
plot(1:length(betadraw1[1,3,]),betadraw1[1,3,])
plot(1:length(betadraw1[1,4,]),betadraw1[1,4,])
plot(1:length(betadraw1[1,5,]),betadraw1[1,5,])
plot(1:length(betadraw1[1,6,]),betadraw1[1,6,])
plot(1:length(betadraw1[1,7,]),betadraw1[1,7,])
plot(1:length(betadraw1[1,8,]),betadraw1[1,8,])
plot(1:length(betadraw1[1,9,]),betadraw1[1,9,])
plot(1:length(betadraw1[1,10,]),betadraw1[1,10,])
plot(1:length(betadraw1[1,11,]),betadraw1[1,11,])
plot(1:length(betadraw1[1,12,]),betadraw1[1,12,])
plot(1:length(betadraw1[1,13,]),betadraw1[1,13,])
plot(1:length(betadraw1[1,14,]),betadraw1[1,14,])

#100th person
plot(1:length(betadraw1[100,1,]),betadraw1[100,1,])
plot(1:length(betadraw1[100,2,]),betadraw1[100,2,])
plot(1:length(betadraw1[100,3,]),betadraw1[100,3,])
plot(1:length(betadraw1[100,4,]),betadraw1[100,4,])
plot(1:length(betadraw1[100,5,]),betadraw1[100,5,])
plot(1:length(betadraw1[100,6,]),betadraw1[100,6,])
plot(1:length(betadraw1[100,7,]),betadraw1[100,7,])
plot(1:length(betadraw1[100,8,]),betadraw1[100,8,])
plot(1:length(betadraw1[100,9,]),betadraw1[100,9,])
plot(1:length(betadraw1[100,10,]),betadraw1[100,10,])
plot(1:length(betadraw1[100,11,]),betadraw1[100,11,])
plot(1:length(betadraw1[100,12,]),betadraw1[100,12,])
plot(1:length(betadraw1[100,13,]),betadraw1[100,13,])
plot(1:length(betadraw1[100,14,]),betadraw1[100,14,])

#200th person
plot(1:length(betadraw1[200,1,]),betadraw1[200,1,])
plot(1:length(betadraw1[200,2,]),betadraw1[200,2,])
plot(1:length(betadraw1[200,3,]),betadraw1[200,3,])
plot(1:length(betadraw1[200,4,]),betadraw1[200,4,])
plot(1:length(betadraw1[200,5,]),betadraw1[200,5,])
plot(1:length(betadraw1[200,6,]),betadraw1[200,6,])
plot(1:length(betadraw1[200,7,]),betadraw1[200,7,])
plot(1:length(betadraw1[200,8,]),betadraw1[200,8,])
plot(1:length(betadraw1[200,9,]),betadraw1[200,9,])
plot(1:length(betadraw1[200,10,]),betadraw1[200,10,])
plot(1:length(betadraw1[200,11,]),betadraw1[200,11,])
plot(1:length(betadraw1[200,12,]),betadraw1[200,12,])
plot(1:length(betadraw1[200,13,]),betadraw1[200,13,])
plot(1:length(betadraw1[200,14,]),betadraw1[200,14,])

#5th person
plot(1:length(betadraw1[5,1,]),betadraw1[5,1,])
plot(1:length(betadraw1[5,2,]),betadraw1[5,2,])
plot(1:length(betadraw1[5,3,]),betadraw1[5,3,])
plot(1:length(betadraw1[5,4,]),betadraw1[5,4,])
plot(1:length(betadraw1[5,5,]),betadraw1[5,5,])
plot(1:length(betadraw1[5,6,]),betadraw1[5,6,])
plot(1:length(betadraw1[5,7,]),betadraw1[5,7,])
plot(1:length(betadraw1[5,8,]),betadraw1[5,8,])
plot(1:length(betadraw1[5,9,]),betadraw1[5,9,])
plot(1:length(betadraw1[5,10,]),betadraw1[5,10,])
plot(1:length(betadraw1[5,11,]),betadraw1[5,11,])
plot(1:length(betadraw1[5,12,]),betadraw1[5,12,])
plot(1:length(betadraw1[5,13,]),betadraw1[5,13,])
plot(1:length(betadraw1[5,14,]),betadraw1[5,14,])

```

=======================================================================
STEP2 - Ends              
=======================================================================


=======================================================================
STEP3 - Starts              
=======================================================================

Study the Beta Distribution
---------------------------
Based on the plots drawn for 21st & 57th respondents.
All the variables have relatively normal distribution.
So, we can use function Mean on the Beta Values.

```{r}

plot(density(betadraw1[21,1,601:1000],width=2)) 
plot(density(betadraw1[21,2,601:1000],width=2))
plot(density(betadraw1[21,3,601:1000],width=2)) 
plot(density(betadraw1[21,5,601:1000],width=2)) 
plot(density(betadraw1[21,6,601:1000],width=2))
plot(density(betadraw1[21,7,601:1000],width=2))
plot(density(betadraw1[21,8,601:1000],width=2))
plot(density(betadraw1[21,9,601:1000],width=2))
plot(density(betadraw1[21,10,601:1000],width=2))
plot(density(betadraw1[21,11,601:1000],width=2))
plot(density(betadraw1[21,12,601:1000],width=2))
plot(density(betadraw1[21,13,601:1000],width=2))
plot(density(betadraw1[21,14,601:1000],width=2))

plot(density(betadraw1[57,1,601:1000],width=2)) 
plot(density(betadraw1[57,2,601:1000],width=2))
plot(density(betadraw1[57,3,601:1000],width=2)) 
plot(density(betadraw1[57,4,601:1000],width=2)) 
plot(density(betadraw1[57,5,601:1000],width=2)) 
plot(density(betadraw1[57,6,601:1000],width=2))
plot(density(betadraw1[57,7,601:1000],width=2))
plot(density(betadraw1[57,8,601:1000],width=2))
plot(density(betadraw1[57,9,601:1000],width=2))
plot(density(betadraw1[57,10,601:1000],width=2))
plot(density(betadraw1[57,11,601:1000],width=2))
plot(density(betadraw1[57,12,601:1000],width=2))
plot(density(betadraw1[57,13,601:1000],width=2))
plot(density(betadraw1[57,14,601:1000],width=2))


par(mfrow=c(3,3))
plot(density(betadraw1[21,8,601:1000],width=2))
plot(density(betadraw1[57,8,601:1000],width=2))
plot(density(betadraw1[180,8,601:1000],width=2))
par(mfrow=c(1,1))
plot(density(betadraw1[180,8,601:1000],width=2))

```

=======================================================================
STEP3 - Ends              
=======================================================================


=======================================================================
STEP4 - Starts              
=======================================================================

Computing BetaMeans for each respondent
---------------------------------------


```{r}
betameans1=apply(betadraw1[,,601:1000],c(1,2),mean)
dim(betameans1)
head(betameans1)

#Calculate LogOdd/Probability for each respondent's model
xbeta1=X.matrix%*%t(betameans1)
dim(xbeta1)
head(xbeta1)
xbeta1=matrix(xbeta1,ncol=3,byrow=TRUE)
dim(xbeta1)
head(xbeta1)

expxbeta1=exp(xbeta1)
dim(expxbeta1)
head(expxbeta1)

rsumvec1=rowSums(expxbeta1) 
pchoicemat1=expxbeta1/rsumvec1 
dim(pchoicemat1)
head(pchoicemat1)

custchoice1 <- max.col(pchoicemat1)
str(custchoice1) # Vector of customer choices for each subject
head(custchoice1)

m1 <- matrix(custchoice1, nrow =36,  byrow=F)
mt1 <- t(m1)
dim(mt1)
apply(mt1, 2, function(x){tabulate(na.omit(x))})

```

=======================================================================
STEP4 - Ends              
=======================================================================


=======================================================================
STEP5 - Starts              
=======================================================================

Validate the Model using Training Data
---------------------------------------
Percent Accuracy: 88.29271 (88.3%)
Area under the ROC curve: 0.8645
```{r}
## Confusion Matrix
ydatavec <- as.vector(t(ydata))
conf.matrix1 = table(custchoice1,ydatavec)
conf.matrix1

str(conf.matrix1)
head(conf.matrix1)
dim(conf.matrix1)

## Calculate percent accuracy
pred.success1 = 0
pred.total1   = 0
for (i in 1:nrow(conf.matrix1)) {
  for (j in 1:ncol(conf.matrix1)) {
    if (i==j) {
        pred.success1 = pred.success1 + conf.matrix1[i,j]
    }
    pred.total1 = pred.total1 + conf.matrix1[i,j]
  }
}

perc.accuracy1 = (pred.success1/pred.total1)*100
perc.accuracy1

## ROC Curve
require("pROC")
roctest1 <- roc(ydatavec, custchoice1, plot=TRUE)    ### ROC curve
auc(roctest1)                       

```

=======================================================================
STEP5 - Ends              
=======================================================================


=======================================================================
STEP7 - Starts              
=======================================================================

Develop One Predictive Model
(Using Mean of all Coefficents of each Beta)
--------------------------------------------


```{r}
#We can get a matrix of coefficient means by respondent
betameansoverall1 <- apply(betadraw1[,,601:1000],c(2),mean) 
betameansoverall1

perc1 <- apply(betadraw1[,,601:1000],2,quantile,probs=c(0.05,0.10,0.25,0.5 ,0.75,0.90,0.95))
perc1

```

=======================================================================
STEP7 - Ends              
=======================================================================


=======================================================================
STEP8 - Starts              
=======================================================================

Predict scenarios with the model (MODEL1)
----------------------------------------------------
Accuracy Percent: 94.4%

```{r}
betavec1=matrix(betameansoverall1,ncol=1,byrow=TRUE)
xbeta1=X.matrix%*%(betavec1)
dim(xbeta1)
xbeta1=matrix(xbeta1,ncol=3,byrow=TRUE)
dim(xbeta1)

expxbeta1=exp(xbeta1)
dim(expxbeta1)
head(expxbeta1)

rsumvec1=rowSums(expxbeta1) 
pchoicemat1=expxbeta1/rsumvec1 
dim(pchoicemat1)
head(pchoicemat1)

pchoicematrnd1 <- round(pchoicemat1*100,digits=0)
pchoicematrnd1
write.csv(pchoicematrnd1,"predict1_matrix.csv")

resp = apply(resp.data.v3[4:39], 2, function(x){tabulate(na.omit(x))}) 
t.resp = t(resp)
write.csv(t.resp,"response_matrix.csv")

```

=======================================================================
STEP8 - Ends              
=======================================================================

=======================================================================
STEP9 - Starts              
=======================================================================

Predict extra scenarios with the model (MODEL1)
-----------------------------------------------------------

ChoiceSet1: Choose Choice2 (69%)
ChoiceSet2: Choose Choice1 (51%)

```{r}
ex_scen <- read.csv("extra-scenarios.csv")
str(ex_scen)
Xextra.matrix <- as.matrix(ex_scen[,c("V1","V2","V3","V4","V5","V6","V7","V8","V9","V10","V11","V12","V13","V14")])
dim(Xextra.matrix)

betavec.extra1=matrix(betameansoverall1,ncol=1,byrow=TRUE)
xextrabeta1=Xextra.matrix%*%(betavec.extra1)
xextrabeta1=matrix(xextrabeta1,ncol=3,byrow=TRUE)
dim(xextrabeta1)

expxbetaextra1=exp(xextrabeta1)
rsumvec.extra1=rowSums(expxbetaextra1)
pchoicemat.extra1=expxbetaextra1/rsumvec.extra1
pchoicemat.extra1 

pchoicemat.extra1.rnd1 <- round(pchoicemat.extra1*100,digits=0)
pchoicemat.extra1.rnd1

```

=======================================================================
STEP9 - Ends              
=======================================================================



=======================================================================
STEP10 - Starts              
=======================================================================
1) Prepare the Full Model
2) Comparisons of Levels in each attribute
3) Imapct of Interaction between Brand/Price
4) Parts-Worth plot - R Plot/Excel Plot

```{r, echo=FALSE}
plot(betameansoverall1)
barplot(betameansoverall1)
```

=======================================================================
STEP10 - Ends              
=======================================================================

=======================================================================
STEP11 - Starts              
=======================================================================

Perform All the steps (1-8) with Model Ownership Covariate - MODEL2
If MODEL2 performs better thah MODEL1, do step# 9,10
--------------------------------------------------------------------


DETERMINE COVARIATE
-------------------
There is a variable in the respondent data set called vList3. Recode this into a variable that is equal to 1 if a respondent has ever owned an STC product. Otherwise, make it equal to zero. 

```{r}
zowner <- 1 * (!is.na(resp.data.v3$vList3))
```

Fit The Model
-------------

```{r}
require(bayesm)
zownertest=matrix(scale(zowner,scale=FALSE),ncol=1)
dim(zownertest)
Data2=list(p=3,lgtdata=lgtdata,Z=zownertest) # p:number of choice alternatives = 3 
mcmctest2=list(R=100000,keep=100)
set.seed(123)
testrun2=rhierMnlDP(Data=Data2,Mcmc=mcmctest2)

```

Analyzing Results (Model With Covariate) - MODEL2
-------------------------------------------------

```{r}
names(testrun2)
betadraw2=testrun2$betadraw
dim(betadraw2)
```

Determine Burn-In Period
------------------------
Based on the graph for 4 respondents:
Burn-In Period = 801

```{r}
#3rd person
plot(1:length(betadraw2[3,1,]),betadraw2[3,1,])
plot(1:length(betadraw2[3,2,]),betadraw2[3,2,])
plot(1:length(betadraw2[3,3,]),betadraw2[3,3,])
plot(1:length(betadraw2[3,4,]),betadraw2[3,4,])
plot(1:length(betadraw2[3,5,]),betadraw2[3,5,])
plot(1:length(betadraw2[3,6,]),betadraw2[3,6,])
plot(1:length(betadraw2[3,7,]),betadraw2[3,7,])
plot(1:length(betadraw2[3,8,]),betadraw2[3,8,])
plot(1:length(betadraw2[3,9,]),betadraw2[3,9,])
plot(1:length(betadraw2[3,10,]),betadraw2[3,10,])
plot(1:length(betadraw2[3,11,]),betadraw2[3,11,])
plot(1:length(betadraw2[3,12,]),betadraw2[3,12,])
plot(1:length(betadraw2[3,13,]),betadraw2[3,13,])
plot(1:length(betadraw2[3,14,]),betadraw2[3,14,])

#120th person
plot(1:length(betadraw2[120,1,]),betadraw2[120,1,])
plot(1:length(betadraw2[120,2,]),betadraw2[120,2,])
plot(1:length(betadraw2[120,3,]),betadraw2[120,3,])
plot(1:length(betadraw2[120,4,]),betadraw2[120,4,])
plot(1:length(betadraw2[120,5,]),betadraw2[120,5,])
plot(1:length(betadraw2[120,6,]),betadraw2[120,6,])
plot(1:length(betadraw2[120,7,]),betadraw2[120,7,])
plot(1:length(betadraw2[120,8,]),betadraw2[120,8,])
plot(1:length(betadraw2[120,9,]),betadraw2[120,9,])
plot(1:length(betadraw2[120,10,]),betadraw2[120,10,])
plot(1:length(betadraw2[120,11,]),betadraw2[120,11,])
plot(1:length(betadraw2[120,12,]),betadraw2[120,12,])
plot(1:length(betadraw2[120,13,]),betadraw2[120,13,])
plot(1:length(betadraw2[120,14,]),betadraw2[120,14,])

#230th person
plot(1:length(betadraw2[230,1,]),betadraw2[230,1,])
plot(1:length(betadraw2[230,2,]),betadraw2[230,2,])
plot(1:length(betadraw2[230,3,]),betadraw2[230,3,])
plot(1:length(betadraw2[230,4,]),betadraw2[230,4,])
plot(1:length(betadraw2[230,5,]),betadraw2[230,5,])
plot(1:length(betadraw2[230,6,]),betadraw2[230,6,])
plot(1:length(betadraw2[230,7,]),betadraw2[230,7,])
plot(1:length(betadraw2[230,8,]),betadraw2[230,8,])
plot(1:length(betadraw2[230,9,]),betadraw2[230,9,])
plot(1:length(betadraw2[230,10,]),betadraw2[230,10,])
plot(1:length(betadraw2[230,11,]),betadraw2[230,11,])
plot(1:length(betadraw2[230,12,]),betadraw2[230,12,])
plot(1:length(betadraw2[230,13,]),betadraw2[230,13,])
plot(1:length(betadraw2[230,14,]),betadraw2[230,14,])

#70th person
plot(1:length(betadraw2[70,1,]),betadraw2[70,1,])
plot(1:length(betadraw2[70,2,]),betadraw2[70,2,])
plot(1:length(betadraw2[70,3,]),betadraw2[70,3,])
plot(1:length(betadraw2[70,4,]),betadraw2[70,4,])
plot(1:length(betadraw2[70,5,]),betadraw2[70,5,])
plot(1:length(betadraw2[70,6,]),betadraw2[70,6,])
plot(1:length(betadraw2[70,7,]),betadraw2[70,7,])
plot(1:length(betadraw2[70,8,]),betadraw2[70,8,])
plot(1:length(betadraw2[70,9,]),betadraw2[70,9,])
plot(1:length(betadraw2[70,10,]),betadraw2[70,10,])
plot(1:length(betadraw2[70,11,]),betadraw2[70,11,])
plot(1:length(betadraw2[70,12,]),betadraw2[70,12,])
plot(1:length(betadraw2[70,13,]),betadraw2[70,13,])
plot(1:length(betadraw2[70,14,]),betadraw2[70,14,])

```

Study the Beta Distribution
---------------------------
Based on the plots drawn for 51st & 100th respondents.
All the variables have relatively normal distribution.
So, we can use function Mean on the Beta Values.

```{r}

plot(density(betadraw2[51,1,801:1000],width=2)) 
plot(density(betadraw2[51,2,801:1000],width=2))
plot(density(betadraw2[51,3,801:1000],width=2)) 
plot(density(betadraw2[51,4,801:1000],width=2)) 
plot(density(betadraw2[51,5,801:1000],width=2)) 
plot(density(betadraw2[51,6,801:1000],width=2))
plot(density(betadraw2[51,7,801:1000],width=2))
plot(density(betadraw2[51,8,801:1000],width=2))
plot(density(betadraw2[51,9,801:1000],width=2))
plot(density(betadraw2[51,10,801:1000],width=2))
plot(density(betadraw2[51,11,801:1000],width=2))
plot(density(betadraw2[51,12,801:1000],width=2))
plot(density(betadraw2[51,13,801:1000],width=2))
plot(density(betadraw2[51,14,801:1000],width=2))

plot(density(betadraw2[100,1,801:1000],width=2)) 
plot(density(betadraw2[100,2,801:1000],width=2))
plot(density(betadraw2[100,3,801:1000],width=2)) 
plot(density(betadraw2[100,4,801:1000],width=2)) 
plot(density(betadraw2[100,5,801:1000],width=2)) 
plot(density(betadraw2[100,6,801:1000],width=2))
plot(density(betadraw2[100,7,801:1000],width=2))
plot(density(betadraw2[100,8,801:1000],width=2))
plot(density(betadraw2[100,9,801:1000],width=2))
plot(density(betadraw2[100,10,801:1000],width=2))
plot(density(betadraw2[100,11,801:1000],width=2))
plot(density(betadraw2[100,12,801:1000],width=2))
plot(density(betadraw2[100,13,801:1000],width=2))
plot(density(betadraw2[100,14,801:1000],width=2))

par(mfrow=c(3,3))
plot(density(betadraw2[21,8,601:1000],width=2))
plot(density(betadraw2[53,8,601:1000],width=2))
plot(density(betadraw2[125,8,601:1000],width=2))
par(mfrow=c(1,1))

```

Computing BetaMeans for each respondent
---------------------------------------

```{r}
betameans2=apply(betadraw2[,,801:1000],c(1,2),mean)
dim(betameans2)
head(betameans2)

#Calculate LogOdd/Probability for each respondent's model
xbeta2=X.matrix%*%t(betameans2)
dim(xbeta2)
head(xbeta2)
xbeta2=matrix(xbeta2,ncol=3,byrow=TRUE)
dim(xbeta2)
head(xbeta2)

expxbeta2=exp(xbeta2)
dim(expxbeta2)
head(expxbeta2)

rsumvec2=rowSums(expxbeta2) 
pchoicemat2=expxbeta2/rsumvec2 
dim(pchoicemat2)
head(pchoicemat2)

custchoice2 <- max.col(pchoicemat2)
str(custchoice2) # Vector of customer choices for each subject
head(custchoice2)

m2 <- matrix(custchoice2, nrow =36,  byrow=F)
mt2 <- t(m1)
dim(mt2)
apply(mt2, 2, function(x){tabulate(na.omit(x))})

```

Validate the Model using Training Data
---------------------------------------
Percent Accuracy: 88.43029 (88.4%)
Area under the ROC curve: 0.8686

```{r}
## Confusion Matrix
ydatavec <- as.vector(t(ydata))
conf.matrix2 = table(custchoice2,ydatavec)
conf.matrix2

str(conf.matrix2)
head(conf.matrix2)
dim(conf.matrix2)

## Calculate percent accuracy
pred.success2 = 0
pred.total2   = 0
for (i in 1:nrow(conf.matrix2)) {
  for (j in 1:ncol(conf.matrix2)) {
    if (i==j) {
        pred.success2 = pred.success2 + conf.matrix2[i,j]
    }
    pred.total2 = pred.total2 + conf.matrix2[i,j]
  }
}

perc.accuracy2 = (pred.success2/pred.total2)*100
perc.accuracy2

## ROC Curve
require("pROC")
roctest2 <- roc(ydatavec, custchoice2, plot=TRUE)    ### ROC curve
auc(roctest2)                       

```

Develop One Predictive Model
(Using Mean of all Coefficents of each Beta)
--------------------------------------------

```{r}
#We can get a matrix of coefficient means by respondent
betameansoverall2 <- apply(betadraw2[,,801:1000],c(2),mean) 
betameansoverall2
write.csv(betameansoverall2,"model2_coeff.csv")

perc2 <- apply(betadraw2[,,801:1000],2,quantile,probs=c(0.05,0.10,0.25,0.5 ,0.75,0.90,0.95))
perc2
```

Predict scenarios with the model (MODEL2)
-----------------------------------------
Accuracy Percent: 94.4%

```{r}
betavec2=matrix(betameansoverall2,ncol=1,byrow=TRUE)
xbeta2=X.matrix%*%(betavec2)
dim(xbeta2)
xbeta2=matrix(xbeta2,ncol=3,byrow=TRUE)
dim(xbeta2)

expxbeta2=exp(xbeta2)
dim(expxbeta2)
head(expxbeta2)

rsumvec2=rowSums(expxbeta2) 
pchoicemat2=expxbeta2/rsumvec2 
dim(pchoicemat2)
head(pchoicemat2)

pchoicematrnd2 <- round(pchoicemat2*100,digits=0)
pchoicematrnd2
write.csv(pchoicematrnd2,"predict2_matrix.csv")

custchoice2 = max.col(pchoicematrnd2)
mat.custchoice2 = matrix(custchoice2,nrow=36,ncol=1)
write.csv(mat.custchoice2,"custChoice2_matrix.csv")



resp = apply(resp.data.v3[4:39], 2, function(x){tabulate(na.omit(x))}) 
t.resp = t(resp)
write.csv(t.resp,"response_matrix.csv")

deltradraw2 = apply(testrun2$Deltadraw[801:1000,],2,mean)
write.csv(deltradraw2,"delta2_matrix.csv")


```

Predict extra scenarios with the model (MODEL2)
-----------------------------------------------------------
ChoiceSet1: Choose Choice2 (71%)
ChoiceSet2: Choose Choice1 (53%)

```{r}
ex_scen <- read.csv("extra-scenarios.csv")
str(ex_scen)
Xextra.matrix <- as.matrix(ex_scen[,c("V1","V2","V3","V4","V5","V6","V7","V8","V9","V10","V11","V12","V13","V14")])
dim(Xextra.matrix)

betavec.extra2=matrix(betameansoverall2,ncol=1,byrow=TRUE)
xextrabeta2=Xextra.matrix%*%(betavec.extra2)
xextrabeta2=matrix(xextrabeta2,ncol=3,byrow=TRUE)
dim(xextrabeta2)

expxbetaextra2=exp(xextrabeta2)
rsumvec.extra2=rowSums(expxbetaextra2)
pchoicemat.extra2=expxbetaextra2/rsumvec.extra2
pchoicemat.extra2 

pchoicemat.extra2.rnd2 <- round(pchoicemat.extra2*100,digits=0)
pchoicemat.extra2.rnd2

custchoice.extra2 = max.col(pchoicemat.extra2.rnd2)
mat.custchoice.extra2 = matrix(custchoice.extra2,nrow=2,ncol=1)
write.csv(mat.custchoice.extra2,"Extra_custChoice2_matrix.csv")

```

Predict My extra scenarios with the model (MODEL2)
-----------------------------------------------------------
MyChoiceSet1: Choose Choice3 (75%)
MyChoiceSet2: Choose Choice3 (41%)

```{r}
my_task = read.csv("Myextra-scenarios-v3.csv")
my_task.mat <- as.matrix(my_task[, c("screen", "RAM", "processor", "price", "brand")])
dim(my_task.mat)
head(my_task.mat)


X.my_task.mat=efcode.attmat.f(my_task.mat)  
dim(X.my_task.mat)
head(X.my_task.mat)

my_task.pricevec=my_task$price-mean(my_task$price)
head(my_task.pricevec)

X.my_task.brands=X.my_task.mat[,9:11]
X.my_task.BrandByPrice = X.my_task.brands*my_task.pricevec
X.my_task.matrix=cbind(X.my_task.mat,X.my_task.BrandByPrice)
dim(X.my_task.matrix)
head(X.my_task.matrix)

betavec.myextra2=matrix(betameansoverall2,ncol=1,byrow=TRUE)
myxextrabeta2=X.my_task.matrix%*%(betavec.myextra2)
myxextrabeta2=matrix(myxextrabeta2,ncol=3,byrow=TRUE)
dim(myxextrabeta2)

myexpxbetaextra2=exp(myxextrabeta2)
rsumvec.myextra2=rowSums(myexpxbetaextra2)
pchoicemat.myextra2=myexpxbetaextra2/rsumvec.myextra2
pchoicemat.myextra2








```



1) Prepare the Full Model
2) Comparisons of Levels in each attribute
3) Imapct of Interaction between Brand/Price
4) Parts-Worth plot - R Plot/Excel Plot

```{r, echo=FALSE}
plot(betameansoverall2)
barplot(betameansoverall2)
```

=======================================================================
STEP11 - Ends              
=======================================================================
